---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/zamorarr/wmata.svg?branch=master)](https://travis-ci.org/zamorarr/wmata)

# wmata

This package provides a R interface to the Washington Metropolitan Area Transit Authority (WMATA) [API](https://developer.wmata.com/)

## Usage
You can use this interface to query the WMATA API. For example, you can get the real time predictions for train arrivals at Metro Center (code A01):

```{r example}
library(wmata)

# get data
j <- next_trains("A01")

# show just the first 3 results
str(j$Trains[1:3], 2)
```

A data frame with mappings from stations to station codes is provided as the object `stations`:

```{r}
head(stations[c("Code", "Name")], 10)
```

## Installation

You can install the released version of wmata from [GitHub](https://github.com/zamorarr/wmata) with:

```{r eval=FALSE}
devtools::install_github("zamorarr/wmata")
```

You will also have to sign up for a WMATA developer key at [https://developer.wmata.com/](https://developer.wmata.com/). Once you get a key, edit your .Renviron file and place this line in there (replacing XXX with your key):

```sh
WMATA_KEY=XXXXXXX
```

You can use `usethis::edit_r_environ()` to edit your .Renviron file.
